The Coin Flip Effect

### 2024-11-03 paper/paper.qmd

---
title: "The Coin Flip Effect"
subtitle: "How Swing States Create Election Outcomes That Resemble The Likelihood of a Coin Flip"
author: 
  - Tara Chakkithara
  - Sakura Hu
  - Luka Tosic
thanks: "Code and data are available at: https://github.com/LukaTosic09/Forecasting-2024-Election"
date: today
date-format: long
abstract: "This paper employs the poll of polls method to develop a bayesian hierarcical model to predict the outcome of the 2024 US general election. Our analysis, based on polling data up to October 19, 20204, indicates that Kamala Harris is predicted to win the election. Modeling election outcomes in the United States poses challenges due to the complexities of the electoral college system, this study specifically focuses on the electoral college vote rather than the popular vote."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

# Measurement

Lorem Ipsum

>>>>

---
title: "The Coin Flip Effect"
subtitle: "How Swing States Create Election Outcomes That Resemble The Likelihood of a Coin Flip"
author: 
  - Tara Chakkithara
  - Sakura Hu
  - Luka Tosic
  - Tara Chakkithara
thanks: "Code and data are available at: https://github.com/LukaTosic09/Forecasting-2024-Election"
date: today
date-format: long
abstract: "This paper employs the poll of polls method to develop a bayesian hierarcical model to predict the outcome of the 2024 US general election. Our analysis, based on polling data up to October 19, 20204, indicates that Kamala Harris is predicted to win the election. Modeling election outcomes in the United States poses challenges due to the complexities of the electoral college system, this study specifically focuses on the electoral college vote rather than the popular vote."
format: pdf
number-sections: true
bibliography: references.bib
---

@@
